---
title: "API Token Usage"
output: rmarkdown::html_vignette
---

ChatRBox enables the use of tokens to access protected API services, using distinct workflows depending on whether the API was provided as a base URL or OpenAPI schema URL. Users may input character tokens as named lists via the `token_service` or `token_openapi` parameters, upon chatbot initialization. These are accompanied by corresponding `header_service` and `header_openapi` named lists to depict custom HTTP headers (e.g "X-API-Key"). The names contained within these lists must not only exactly match each other but also match the appropriate service name, since tokens are applied using name-matching. Warnings will be thrown for missing, mismatching or duplicated names.

<br>

### Tokens for API URLs

Here, we demonstrate the initialization of a chatbot named `access` using the Ollama AI provider and `mistral` AI model. A fictitious protected API has been provided as an API base URL via `services_list`. Therefore, the token and token header have been provided as identically named lists using `token_service` and `header_service`, respectively.   

```{r, eval=FALSE}
access <- ChatRBox$new(ai_provider = ellmer::chat_ollama, 
                        base_url = Sys.getenv("OLLAMA_HOST", unset = "http://localhost:11434"),
                        model = Sys.getenv("OLLAMA_MODEL", unset = "mistral")),
                        services_list = list(token = "https://exampleapi/token"),
                        token_service = list(token = "MY_SECRET_TOKEN"),
                        header_service = list(token = "X-API-Key"))
```

<br>

### Tokens for OpenAPI JSON Schema URLs

Here is the equivalent chatbot initialization to provide this protected API service as an OpenAPI JSON schema URL. This method rather creates API client functions, unlike loading APIs via `services_list` which requires a `client_fns` endpoint.

```{r, eval=FALSE}
access <- ChatRBox$new(ai_provider = ellmer::chat_ollama, 
                        base_url = Sys.getenv("OLLAMA_HOST", unset = "http://localhost:11434"),
                        model = Sys.getenv("OLLAMA_MODEL", unset = "mistral")),
                        openapi_list = list(token = "https://exampleapi/token/openapi.json"),
                        token_openapi = list(token = "MY_SECRET_TOKEN"),
                        header_openapi = list(token = "X-API-Key"))
```

Whilst only the `header_service` and `header_openapi` arguments are contained within the chatbot `R6` object for ease, ChatRBox functions also facilitate the use of `auth_scheme` for authorization methods (e.g "Bearer"). Hence, passing authorization methods to AI chatbots requires modification of package source code. 
