---
title: "Providing Tool Functions"
output: rmarkdown::html_vignette
---

### Defining Tool Functions in R

Here, we define a simple addition tool as an R function named `add`, taking the arguments `x` and `y`.

```{r, eval=FALSE}
add <- function(x,y) {
  x + y
} 
```

<br>

### Providing Chatbots with Tool Functions

We add `add` to our existing tools environment by listing this function in the named list `tools_list`, using the `ChatRBox_update()` function.

```{r, eval=FALSE}
ChatRBox_update(object = session, tools_list = list(add_two_numbers = add))
```

Asking our chatbot to use this service for a simple arithmetic results in the `add` tool output, alongside an AI dialogue.

```{r, eval=FALSE}
session$talk("Use a service to compute 70 + 76") 
```

Tool addition works identically to API URL (`services_list`), OpenAPI schema URL (`openapi_list`) and data frame (`data_list`) addition, whereby tools may be defined during chatbot initialization or update. When adding tools via `ChatRBox_update()`, only the tools to be added need be referenced, whilst previously stored tool functions remain accessible.
