---
title: "Chatbot Re-initialization"
output: rmarkdown::html_vignette
---

### When to Re-initialize

Whilst chatbot re-initialization may resolve lagging AI response times or accuracy following long conversations, it is not often required as AI turns facilitate chatbot memory. However, `ChatRBox_update()` does not accommodate changing `ai_provider` or additional properties like `model`, meaning re-initialization may be used to switch AI provider or alter external arguments. 

`ChatRBox_update()` also adds API services, tools and data cumulatively, meaning re-initialization may be used to clear these fields. This may also be achieved for `tools_list` and `data_list` by creating new tools and data environments, respectively.

<br>

### Using Multiple AI Chatbots

Here, we re-initialize `session`, alongside creating another chatbot named `new`. `new` has been instructed to omit the letter 'A' from replies, whereas `session` omits the letter 'E'. Both utilize the `gpt-oss` model in Ollama but are entirely independent, demonstrating the implications of multiple `R6` objects. 

```{r, eval=FALSE}
session <- ChatRBox$new(ai_provider = ellmer::chat_ollama, 
                        base_url = Sys.getenv("OLLAMA_HOST", unset = "http://localhost:11434"),
                        model = Sys.getenv("OLLAMA_MODEL", unset = "mistral")),
                        prompt_template = "Don't include the letter 'E' in your responses")

new <- ChatRBox$new(ai_provider = ellmer::chat_ollama, 
                    base_url = Sys.getenv("OLLAMA_HOST", unset = "http://localhost:11434"),
                    model = Sys.getenv("OLLAMA_MODEL", unset = "mistral")),
                    prompt_template = "Don't include the letter 'A' in your responses")
```

We can interact with either chatbot using `$talk()`, whereby the properties of `session` and `new` are self-contained. These chatbots may be used and updated independently, allowing for simultaneous AI workflows with specialist features (tools, data, APIs, prompts...) and performance comparison. 

Here, we ask our chatbots the same question to compare AI outputs.    

```{r, eval=FALSE}
session$talk("What is the capital of the USA?")

new$talk("What is the capital of the USA?") 
```
